### 2011-12-02 AffineLieAlgebras/Thesis/3.tex
Translation of chapter 4 started

\begin{abstract}
Splint of root system for simple Lie algebra appears naturally in
studies of (regular) embeddings of reductive subalgebras. Splint can
be used to construct branching rules. We demonstrate that 
splint properties implementation drastically simplify calculations of
branching coefficients.
\end{abstract}

\section{Introduction}
\label{sec:Introduction}

Embedding $\phi$ of a root system $\Delta_1$ into a root system
$\Delta$ is a bijective map of roots of $\Delta_{1}$ to a (proper)
subset of $\Delta$ that commutes with vector composition law in
$\Delta_{1}$ and $\Delta$.
\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Note that the image $Im(\phi)$ must not inherit the root system
properties except the addition rules equivalent to the addition
rules in $\Delta_{1}$ (for pre-images). Two embeddings $\phi_1$ and $\phi_2$  
can splinter $\Delta$  when the latter can be presented 
as a disjoint union of images $Im(\phi_1)$ and $Im(\phi_2)$.   
The term {\it splint} was
introduced by D. Richter in  \cite{richter2008splints} where the
classification of splints for simple Lie algebras was obtained.
There was also mentioned that splint must have tight
connections with the injection fan construction. The fan $\Gamma
\subset \Delta$ was
introduced in \cite{lyakhovsky1996rra} as a subset of root system describing recurrent
properties of branching coefficients for maximal embeddings. Injection fan is an
efficient tool to study branching rules. Later this construction
was generalized to non-maximal embeddings and infinite-dimensional
Lie algebras in \cite{2010arXiv1007.0318L, ilyin812pbc}.

In the present paper we study connections between splint and
injection fan for regular embedding of reductive subalgebras
${\mathfrak a}$ in simple Lie algebra $\mathfrak{g}$. We show that (under
certain conditions described in section \ref{sec:stems and
multiplicity functions}) splint is a natural tool to study
reduction properties of ${\mathfrak g}$-modules
with respect to a subalgebra ${\mathfrak a}\longrightarrow
{\mathfrak g}$. Using this tool we obtain the main result -- the one-to-one correspondence between weight
multiplicities in irreducible modules of splint and branching
coefficients for a reduced module $L^{\mu}_{{\mathfrak
g}\downarrow {\mathfrak a}}$.

\section{Injections and splints}

>>>>

Сплинт корневой системы простой алгебры Ли возникает при изучении регулярных вложений редуктивных подалгебр. Сплинт можно использовать для получения правил ветвления. Мы показываем, что использование свойств сплинта  позволяет сильно упростить вычисление коэффициентов ветвления.

\section{Введение}
\label{sec:Introduction}

Вложение  $\phi$ корневой системы $\Delta_1$ в корневую систему $\Delta$ -- это биективное отображение корней из $\Delta_{1}$ в (собственное) подмножество $\Delta$, коммутирующее с законом сложения векторов в $\Delta_{1}$ и $\Delta$.

\begin{equation*}
\phi:\Delta_1 \longrightarrow \Delta
\end{equation*}
\begin{equation*}
\phi \circ (\alpha + \beta) =\phi \circ \alpha + \phi \circ \beta,
\,\,\, \alpha,\beta \in \Delta_1
\end{equation*}

Заметим, что образ  $Im(\phi)$ не обязан обладать свойствами корневой системы за исключением правил сложения, эквивалентных правилам сложения в  $\Delta_{1}$ (для прообразов). Два вложения  $\phi_1$ и $\phi_2$  {\it расщепляют} корневую систему  $\Delta$ если она может быть представлена, как несвязное объединение образов $Im(\phi_1)$ и $Im(\phi_2)$.   
Термин {\it сплинт} (расщепление) предложил D. Richter в работе  \cite{richter2008splints}, где  были получены все сплинты для простых алгебр Ли. В работе так же упоминалось, что сплинт должен быть тесно связан с конструкцией веера вложения. Веер вложения  $\Gamma\subset \Delta$ был введен в работе  \cite{lyakhovsky1996rra} как подмножество корневой системы, описывающее рекуррентные свойства коэффициентов ветвления для максимальных вложений. Веер вложения -- это эффективный инструмент для изучения правил ветвления. Позднее в работах \cite{2010arXiv1007.0318L, ilyin812pbc} эта конструкция была обобщена на не-максимальные вложения и бесконечномерные алгебры Ли.

В данной главе мы изучаем связь между сплинтом и веером вложения для регулярных вложений редуктивных подалгебр ${\mathfrak a}$ в простую алгебру Ли $\mathfrak{g}$. Мы демонстрируем, что (при выполнении определенных условий, описанных в разделе \ref{sec:stems and multiplicity functions}) сплинт является естественным инструментом для изучения свойств редукции  $\gf$-модулей по отношению к подалгебре $\af\longrightarrow\gf$. Используя этот инструмент мы получаем основной результат данной главы -- однозначное соответствие между кратностями весов неприводимых модулей сплинта и коэффициентов ветвления для редуцированного модуля $L^{\mu}_{\gf\downarrow \af}$

\section{Вложения и сплинты}
